Effects of epidemiological structure on the transient evolution of HIV virulence

### 2016-10-26 ms/S1_appendix.tex
tweaks

\bibliography{virulence}
\end{document}

>>>>

\begin{thebibliography}{1}

\bibitem{champredon_hiv_2013}
Champredon D, Bellan S, Dushoff J.
\newblock {HIV} Sexual Transmission Is Predominantly Driven by Single
  Individuals Rather than Discordant Couples: A Model-Based Approach.
\newblock PLoS ONE. 2013;8(12):e82906.
\newblock doi:{10.1371/journal.pone.0082906}.

\bibitem{shirreff_transmission_2011}
Shirreff G, Pellis L, Laeyendecker O, Fraser C.
\newblock Transmission Selects for {HIV-1} Strains of Intermediate Virulence: A
  Modelling Approach.
\newblock PLoS Computational Biology. 2011;7(10):e1002185.
\newblock doi:{10.1371/journal.pcbi.1002185}.

\bibitem{hollingsworth_hiv1_2008}
Hollingsworth TD, Anderson RM, Fraser C.
\newblock {HIV}-1 Transmission, by Stage of Infection.
\newblock Journal of Infectious Diseases. 2008;198(5):687--693.
\newblock doi:{10.1086/590501}.

\bibitem{may_transmission_1988}
May RM, Anderson RM.
\newblock The Transmission Dynamics of Human Immunodeficiency Virus (HIV) [and
  Discussion].
\newblock Philosophical Transactions of the Royal Society of London Series B,
  Biological Sciences. 1988;321(1207):565--607.

\bibitem{herbeck_evolution_2016}
Herbeck JT, Mittler JE, Gottlieb GS, Goodreau SM, Murphy JT, Cori A, et~al.
\newblock Evolution of {HIV} virulence in response to widespread scale up of
  antiretroviral therapy: a modeling study.
\newblock Virus Evolution. 2016;2(2):vew028.
\newblock doi:{10.1093/ve/vew028}.

\end{thebibliography}
\end{document}

### 2016-10-26 ms/S2_appendix.tex
tweaks

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{../figures/fig_S2_2.pdf}
\caption{{\bf Envelopes of progression trajectories under all models.}
This figure matches Fig 2 in main text, but displays the
envelope of \Lspvl\ rather than expected progression time to AIDS over time
for each model.
}
\label{fig:virtraj}
\end{figure}

@@

\begin{figure}[!ht]
  \includegraphics[width=\textwidth]{../figures/fig_S2_3.pdf}
\caption{{\bf Univariate distributions of transmission probabilities and \Lspvl\.}
This figure matches Fig 3 in main text, but displays the
univariate distributions for the transmission probability and 
\Lspvl\ time at the virulence
peak and at the epidemiological equilibrium,
rather than the distributions of progression time to AIDS.
}
\label{fig:tranvirsum}
\end{figure}

>>>>

\renewcommand\thefigure{S\arabic{figure}}

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{../figures/fig_S2_2.pdf}
\caption{{\bf Envelopes of SPVL trajectories under all models.}
This figure matches Fig 2 in main text, but displays the
envelope of \Lspvl\ rather than expected progression time to AIDS over time
for each model.
}
\label{fig:virtraj}
\end{figure}

@@

%% \Lspvl\ doesn't get bolded so I got rid of log10
\begin{figure}[!ht]
  \includegraphics[width=\textwidth]{../figures/fig_S2_3.pdf}
\caption{{\bf Univariate distributions of transmission probabilities and SPVL.}
This figure matches Fig 3 in main text, but displays the
univariate distributions for the transmission probability and \Lspvl\ time at the virulence
peak and at the epidemiological equilibrium,
rather than the distributions of progression time to AIDS.
}
\label{fig:tranvirsum}
\end{figure}
